### 2017-03-31 paper/evaluation.tex
removed old comments
pass on text

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the execution time is
distributed among test cases.  In the third research question, we
investigate if developers consider low-level parallelism features
available out-of-the-box (see Section~\ref{sec:modes}). In addition,
we want to identify what configurations are often used and why they
are more popular (if any).  The fourth research question addresses the
impact of low-level parallelism on test execution from projects in our
sample set. We want to identify subjects that already use test
parallelization and compare their performance in contrast to
sequential execution. In addition, we are interested in evaluating the
performance of sequential test suites with different parallelization
settings.
%%\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
%%addresses the characteristics of regression tests from the previous
%%experiment.  More specifically, we want to investigate if there is a
%%relation between the balance of test execution (\ie, how uniformly
%%distributed is the execution time across tests cases) and the usage of
%%computational resources (\ie, if tests are mostly CPU or IO intense)
%%that impacts the effectiveness of parallelization}.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{Given that
    \percentMedLongRunning{} of the projects are costly (\ie,
    \numMedLong{} projects from \medg{} and \longg{}), we concluded
    that time-consuming regression test suites are relatively frequent
    in open-source projects.}
\end{minipage}
}
\end{center}

@@

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Medium & 17 & 20 & 7 \\
        Long   &  9 & 14 & 5 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

>>>>

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the execution time is
distributed among test cases.  In the third research question, we
investigate if developers consider low-level parallelism features
available out-of-the-box (see Section~\ref{sec:modes}). In addition,
we want to identify what configurations are often used and why they
are more popular (if any).  The fourth research question addresses the
impact of low-level parallelism on test execution from projects in our
sample set. We want to identify subjects that already use test
parallelization and compare their performance in contrast to
sequential execution. In addition, we are interested in evaluating the
performance of sequential test suites with different parallelization
settings.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We concluded that
    time-consuming regression test suites are relatively frequent in
    open-source projects given that \percentMedLongRunning{} of the
    projects are costly (\ie, \numMedLong{} projects from \medg{} and
    \longg{}).}
\end{minipage}
}
\end{center}

@@

    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  9 & 14 & 5 \\
        Medium & 17 & 20 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%
